### 2010-12-29 Documentation/atropos/atropos.tex
ENH:  Minor edit.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@732 fd2da0a4-d968-48df-9cb5-d8c496287cbf

To highlight the
value of this open source contribution, we performed a search of
software attributes on NITRC and found that as of November 2010 no
stand-alone EM methods are currently listed.
%Atropos's memory efficiency enables EM-segmentation of many classes at
%once, a capability that is due to a sparse internal representation of
%prior probability images that minimizes the need for random access
%memory.  
We evaluate EM-based classification of $1 mm^3$ T1 MR
neuroimages into 69 neuroanatomical regions to illustrate the practical
value of the low-memory implementation within this paper.  
Although Atropos may be applied to
multivariate data from arbitrary modalities, we limit our evaluation
to tissue-classification in T1 neuroimaging in part due to the
abundance of ``gold-standard'' data for this modality.  Consistent
with our advocacy of open science (not to mention the facilitation of
analysis due to accessibility) we also only use publicly available
data sets.  For this reason, all results in this paper are
reproducible with the caveat that users may require some guidance from
the authors or other users in the community.

@@

\section{Evaluation}
Atropos~encodes a family of segmentation techniques that may be
instantiated for different applications but here we evaluate only two
of the many possibilites. First, we perform an evaluation on the
BrainWeb dataset using both the standard T1 image with multiple bias
and noise levels and also the BrainWeb20 data
\citep{Aubert-Broche2006a,Battaglini2008}.  In combination, this data
allows one to vary not only noise and bias but also the underlying
anatomy.  Second, we evaluate the use of Atropos in improving whole
brain parcellation and exercise its ability to efficiently solve {\em
many class} expectation maximization problem.  We choose this
evaluation problem in part to illustrate the flexibility of Atropos
and also the benefits of the novel, efficient implementation that
allows many-class problems to be solved with low memory usage ($<$2GB
for a 69 class model on 1mm$^3$ brain data).

@@

to compare performance with the original N3 algorithm \cite{Sled1998}.

>>>>

To highlight the
value of this open source contribution, we performed a search of
software attributes on NITRC and found that as of November 2010 no
stand-alone EM methods are currently listed.
%Atropos's memory efficiency enables EM-segmentation of many classes at
%once, a capability that is due to a sparse internal representation of
%prior probability images that minimizes the need for random access
%memory.  
We evaluate EM-based classification of 1 mm$^3$ T1 MR
neuroimages into 69 neuroanatomical regions to illustrate the practical
value of the low-memory implementation within this paper.  
Although Atropos may be applied to
multivariate data from arbitrary modalities, we limit our evaluation
to tissue-classification in T1 neuroimaging in part due to the
abundance of ``gold-standard'' data for this modality.  Consistent
with our advocacy of open science (not to mention the facilitation of
analysis due to accessibility) we also only use publicly available
data sets.  For this reason, all results in this paper are
reproducible with the caveat that users may require some guidance from
the authors or other users in the community.

@@

\section{Evaluation}
Atropos~encodes a family of segmentation techniques that may be
instantiated for different applications but here we evaluate only two
of the many possibilites. First, we perform an evaluation on the
BrainWeb dataset using both the standard T1 image with multiple bias
and noise levels and also the BrainWeb20 data
\citep{Aubert-Broche2006a,Battaglini2008}.  In combination, this data
allows one to vary not only noise and bias but also the underlying
anatomy.  Second, we evaluate the use of Atropos in improving whole
brain parcellation and exercise its ability to efficiently solve {\em
many class} expectation maximization problem.  We choose this
evaluation problem in part to illustrate the flexibility of Atropos
and also the benefits of the novel, efficient implementation that
allows many-class problems to be solved with low memory usage ($<$2GB
for a 69 class model on 1 mm$^3$ brain data).

@@

to compare performance with the original N3 algorithm \citep{Sled1998}.
